%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{phonenumbers}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
    }

\urlstyle{same}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\large \scshape Mohammed Al-Jawaheri} \\ \vspace{1pt}
       Doha, Qatar $|$ \texttt{+974-50767877}  $|$ mjawaheri02@gmail.com $|$
    \href{https://linkedin.com/in/mohammed-al-jawaheri}{linkedin} $|$
    \href{https://github.com/M-aljawaheri}{github}
\end{center}
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Carnegie Mellon University}{}
      {B.S. in Computer Science, Concentration in Computer systems}{}
      \\ \hfill \phantom{phantom} \hfill May 2025\;\;    \\

  \resumeSubHeadingListEnd
%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Software Engineer Intern}{May 2024 -- Aug 2024}
    {OpenStack Swift, NVIDIA}{}
    \resumeItemListStart
        \resumeItem{Landed \href{https://review.opendev.org/c/openstack/swift/+/921664}{patches} approved by project leads and merged upstream to \href{https://github.com/openstack/swift/commit/6105b38e65b00c23d373e17ad9f89e4243395165}{OpenStack Swift}.}
        \resumeItem{Added quota support features to prevent cluster abuse, enhancing system reliability.}
        \resumeItem{Implemented modern recon features for the container reaper, optimizing performance.}
        \resumeItem{Improved concurrency in the container sharder daemon.}
    \resumeItemListEnd
      
    \resumeSubheading
      {Backend Engineer}{Sep 2022 -- Feb 2024}
      {Hungry Mushrooms Game Studio}{}
      \resumeItemListStart
        \resumeItem{Architected a backend migration for three games from previous backends and ad-hoc Firebase storage, improving scalability and performance.}
        \resumeItem{Oversaw live migration of player NoSQL data to CockroachDB, ensuring data integrity and minimal downtime.}
        \resumeItem{Collaborated with game developers to optimize backend services for enhanced player experiences.}
      \resumeItemListEnd

    \resumeSubheading
      {Teaching Assistant}{Aug 2023 -- Present}
      {Carnegie Mellon University}{}
      \resumeItemListStart
        \resumeItem{Graded and created exams for undergraduate courses on Computer Networks, including assignments on building web servers with WSGI support for Flask and other frameworks.}
        \resumeItem{Assisted students in understanding complex networking concepts and debugging challenging problems.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects and Achievements}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{HyperOS: Operating System \& Hypervisor} $|$ \emph{C/x86 Assembly}}{Aug 2022 -- Jan 2023}
          \resumeItemListStart
          \resumeItem{Built a fully preemptive multitasking kernel on real x86 hardware using C and x86 Assembly.}
          \resumeItem{Supported paravirtualization interfaces for running guest kernels, enhancing system versatility.}
          \resumeItem{Implemented user-space multithreading and hardware exception handling.}
          \resumeItem{Developed custom user-space thread libraries and synchronization primitives, optimizing performance.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{C0++: Type-Inferring Optimizing Compiler} $|$ \emph{C++17, Flex/Bison}}{Aug 2021 -- Jan 2022}
          \resumeItemListStart
            \resumeItem{Built a compiler for a C-like language targeting x86-64 architecture.}
            \resumeItem{Implemented optimizations such as partial redundancy elimination and strength reductions.}
            \resumeItem{Utilized SSA form, achieving performance competitive with GCC -O1 on various benchmarks.}
            \resumeItem{Demonstrated strong problem-solving skills in compiler design and code optimization.}
          \resumeItemListEnd


\resumeProjectHeading
          {\textbf{Personal Website} $|$ \emph{NextJS/ChakraUI} (\href{www.mjawaheri.com}{mjawaheri.com})}{Apr 2023 \-- Present}
          \resumeItemListStart
          \resumeItem{Personal portfolio built using Next 14}
          \resumeItem{Uses ChakraUI for smooth animations \& page transitions }
          \resumeItemListEnd
        

      \resumeProjectHeading
          {\textbf{Liso: HTTP/HTTPS Web Server} $|$ \emph{C}}{Jan 2022 -- May 2022}
          \resumeItemListStart
            \resumeItem{Built a multiplexing HTTP and HTTPS web server in C, supporting HTTP parsing, CGI, WSGI, and TLS connections.}
            \resumeItem{Optimized for high concurrency and performance, stress-tested using Siege and ApacheBench benchmarks.}
          \resumeItemListEnd


    \resumeSubHeadingListEnd
%
%----------- Honors and Awards-----------
\section{Honors and Awards}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Andrew Carnegie Society Scholar}{ Recognition by CMU to 40 exemplary students} \\
     \textbf{Qatar Campus Scholar}{ Recognition given by CMU-Q  given to one graduate of each major} \\
    \textbf{Best Freshman Team}{ prize at CarnegieApps Hackathon 2020}
        } \\
    \textbf{QCPC 2021 winner} { Competed in QCPC, ACPC }
    }
 \end{itemize}


    
%
%-----------PROGRAMMING SKILLS-----------
%\section{Technical Skills}
% \begin{itemize}[leftmargin=0.15in, label={}]
%    \small{\item{
%     \textbf{Languages}{: C/C++17, x86/x86-64 Assembly, ARM Assembly, Java, Javascript, Python, SML.} \\
%     \textbf{Developer Tools}{: Git, Gerrit, Docker, Simics, GDB, CMake} \\
%    }}
% \end{itemize}


%-------------------------------------------
\end{document}
